Neural Neural Textures Make Better Simulators ``I Can't Believe It's Not Real!''

### 2022-06-13 CORL/example.tex
Added main_diagram_beautiful.pdf
Fixed errors
Moved summaries into their subsections

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/first_diagram.pdf}
	\end{center}
	\caption{
		This is an overview of what TRITON accomplishes.
		TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
		}
	\label{fig:uvl_explanation}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
	\end{center}
	\caption{
		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		% $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		%
		%JUNE 12:
		%Don't say 4 main components; say 2 components and 2 losses
		%TODO: Try to use right-angled arrows
		%TODO: Use tau as a function
		%Copy paste the figure multiple times, deleting things
		%Mention "Neural Neural Texture": Its a function mapping UV to RGB
		%Formulation doesnt mentino texture; just uvl inputs and final outputs
		%Always use function notation tau(u,v) instead of just tau (in figure as well) 
		%The arrow should be running through tau. It's not a variable its a function...
		%Rename 'B' to "N" for batch size
		%Figure 8: Align consistent with inconsistent and use all 5 green ones
		%
		This figure is an overview TRITON.
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses.
		Although $\pi\toB$ and $\ph\toB$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

@@

	\begin{enumerate}
		\item{
			Neural Neural Textures $\tau\toL: (u,v) \rightarrow (R,G,B)$:

@@

			These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
			\begin{equation}
				\pi=\tau\toL(s)
			\end{equation}
			We then concatenate the scenes with the projections channelwise to obtain images from domain A: $\ppis \in A$.
		}
		\item{
			Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
			\begin{equation}
				\ph=\Tab(\pis)\ \ \ \text{ and }\ \ \ \ppish=\Tba(p)
			\end{equation}
			$T$ is a variation of MUNIT~\cite{munit}, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
		}
		\item {
			Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene. 
			\begin{equation}
				u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
			\end{equation}
		}
		\item{
			Texture Realism Loss $\lTR$: To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output. 
			\begin{equation}
				\lTR \Rightarrow \pi \approx \ph
			\end{equation}
			As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
		}

	\end{enumerate}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=200pt]{../images/module_translator.pdf}
	\end{center}
	\caption{
		A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
	}
	% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
	% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
	% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
	\label{fig:learnable_textures}
\end{figure}

@@

@@

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=25x0pt]{../images/texture_realism_ablation.pdf}
	\end{center}
	\caption{
		The neural texture looks more realistic with texture realism loss enabled. Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments. 
	}
	\label{fig:texture_realism_ablation}
\end{figure}

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/blurry_recovery.pdf}
		\end{center}
		\caption{
			The recovered texture is more crisp when we have surface consistency losses $\lUC$ and $\lTR$ enabled.
			[[Michael, should I include CycleGAN and other algos here?]]
		}
		\label{fig:unprojection_consistency_loss}
	\end{figure}
	% 	Alphabet Three							
	% 	Masked				Unmasked			
	% 	LPIPS		L2		LPIPS		L2	
	% 	Sync	Unsync	Sync	Unsync	Sync	Unsync	Sync	Unsync
	% Pure MUNIT	0.0437	0.0373	0.00500	0.00490	0.434	0.402	0.0425	0.0392
	% Texture Only	0.0442	0.0386	0.00586	0.00589	0.285	0.255	0.0364	0.0310
	% Texture Reality	0.0286	0.0267	0.00479	0.00478	0.117	0.1157	0.0123	0.0122
	% CycleGAN			TODO: Sync with respect to L2, so sync is always ≥ unsync					
	% CUT				TODO: Google Synthetic Dataset

>>>>

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/first_diagram.pdf}
	\end{center}
	\caption{
		This is an overview of what TRITON accomplishes.
		TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
		}
	\label{fig:first_diagram}
\end{figure}

@@

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_beautiful.pdf}
	\end{center}
	\caption{
		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		% $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		%
		%JUNE 12:
		%Don't say 4 main components; say 2 components and 2 losses
		%TODO: Try to use right-angled arrows
		%TODO: Use tau as a function
		%Copy paste the figure multiple times, deleting things
		%Mention "Neural Neural Texture": Its a function mapping UV to RGB
		%Formulation doesnt mentino texture; just uvl inputs and final outputs
		%Always use function notation tau(u,v) instead of just tau (in figure as well) 
		%The arrow should be running through tau. It's not a variable its a function...
		%Rename 'B' to "N" for batch size
		%Figure 8: Align consistent with inconsistent and use all 5 green ones
		%
		This figure is an overview TRITON.
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses.
		Although $\pi\toB$ and $\ph\toB$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

@@

	Neural Neural Textures $\tau\toL: (u,v) \rightarrow (R,G,B)$:

@@

	These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
	\begin{equation}
		\pi=\tau\toL(s)
	\end{equation}
	We then concatenate the scenes with the projections channelwise to obtain images from domain A: $\ppis \in A$.

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=200pt]{../images/module_translator.pdf}
		\end{center}
		\caption{
			A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
		}
		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
		\label{fig:module_translator}
	\end{figure}

@@

	Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
	\begin{equation}
		\ph=\Tab(\pis)\ \ \ \text{ and }\ \ \ \ppish=\Tba(p)
	\end{equation}
	$T$ is a variation of MUNIT~\cite{munit}, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.

@@

	Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene. 
	\begin{equation}
		u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
	\end{equation}

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
		\end{center}
		\caption{
			The neural texture looks more realistic with texture realism loss enabled. Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments. 
		}
		\label{fig:texture_realism_ablation}
	\end{figure}

	Texture Realism Loss $\lTR$: To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output. 
	\begin{equation}
		\lTR \Rightarrow \pi \approx \ph
	\end{equation}
	As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width=400pt]{../images/blurry_recovery.pdf}
		\end{center}
		\caption{
			The recovered texture is more crisp when we have surface consistency losses $\lUC$ and $\lTR$ enabled.
			[[Michael, should I include CycleGAN and other algos here?]]
		}
		\label{fig:blurry_recovery}
	\end{figure}
	% 	Alphabet Three							
	% 	Masked				Unmasked			
	% 	LPIPS		L2		LPIPS		L2	
	% 	Sync	Unsync	Sync	Unsync	Sync	Unsync	Sync	Unsync
	% Pure MUNIT	0.0437	0.0373	0.00500	0.00490	0.434	0.402	0.0425	0.0392
	% Texture Only	0.0442	0.0386	0.00586	0.00589	0.285	0.255	0.0364	0.0310
	% Texture Reality	0.0286	0.0267	0.00479	0.00478	0.117	0.1157	0.0123	0.0122
	% CycleGAN			TODO: Sync with respect to L2, so sync is always ≥ unsync					
	% CUT				TODO: Google Synthetic Dataset
